%\documentclass[acmtog]{formats/acmart} 
\documentclass[acmtog]{acmart}
\makeatletter
\let\@authorsaddresses\@empty
\makeatother

%\documentclass[10pt, format=manuscript,nonacm]{acmart}

%\documentclass[acmtog,anonymous,review]{acmart}

\usepackage{soul}
\usepackage{booktabs} % For formal tables
\citestyle{acmauthoryear}
\setcitestyle{square}
\usepackage{ifthen}
\usepackage{enumitem}
\usepackage{algorithm}
%\usepackage{algorithmicx}
%\usepackage{algcompatible}
\usepackage[noend]{algpseudocode}
%\usepackage{algorithm2e}
\usepackage{float}
\usepackage{syntax}
\usepackage{amsfonts}
\let\Bbbk\relax
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{xspace}
\usepackage{colortbl}
\usepackage{gensymb}
\usepackage{verbatim}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{cleveref}
\usepackage{pifont}
\usepackage{circledsteps}



%\lstset{style=mystyle}
\newcommand{\etal}{et al.}
\newcommand\TODO[1]{{\color{red} A: #1}}
\newcommand{\yuexin}[1]{{\color{blue} YX: #1}}
\newcommand{\ZY}[1]{{\color{cyan} ZY: #1}}
\newcommand{\manyi}[1]{{\color{brown} MY: #1}}
\newcommand{\haoran}[1]{{\color{olive} HR: #1}}
\newcommand{\yiteng}[1]{{\color{red} YT: #1}}
\newcommand{\yiming}[1]{{\color{orange} YM: #1}}
\newcommand{\changhe}[1]{{\color{orange} CH: #1}}


\usepackage{amsthm,amsmath,amssymb}
\usepackage{mathrsfs}
\usepackage[normalem]{ulem}
\begin{document}
\settopmatter{printacmref=false}
\setcopyright{none}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{empty} 

%\setcopyright{acmlicensed}
%\acmJournal{TOG}
%\acmYear{XXX} \acmVolume{XX} \acmNumber{XX} \acmArticle{XX} \acmMonth{XX} %\acmPrice{15.00}\acmDOI{10.1145/3618324}
\title{SymBridge: A Human-in-the-Loop Cyber-Physical Interactive System for Adaptive Human-Robot Symbiosis}


\author{Haoran Chen}
\authornote{Joint first authors.}
\affiliation{%
  \institution{Shandong University}
  \country{China}
}
\author{Yiteng Xu}
\authornotemark[1]
\affiliation{%
  \institution{ShanghaiTech University}
  \country{China}
}
\author{Yiming Ren, Yaoqin Ye}
\affiliation{%
  \institution{ShanghaiTech University}
  \country{China}
}

\author{Xinran Li, Ning Ding, Yuxuan Wu, Yaoze Liu}
\affiliation{%
  \institution{Shandong University}
  \country{China}
}

\author{Peishan Cong, Ziyi Wang, Bushi Liu, Yuhan Chen}
\affiliation{%
  \institution{ShanghaiTech University}
  \country{China}
}
%\author{Ziyi Wang}
%\affiliation{%
%  \institution{ShanghaiTech University}
%}
%\author{Bushi Liu}
%\affiliation{%
%  \institution{ShanghaiTech University}
%}
%\author{Yuhan Chen}
%\affiliation{%
%  \institution{ShanghaiTech University}
%}
\author{Zhiyang Dou}
\affiliation{%
  \institution{The University of Hong Kong}
  \country{China}
}
\author{Xiaokun Leng}
\affiliation{%
  \institution{LEJU(Shenzhen) Robotics Co., Ltd}
  \country{China}
}
\author{Manyi Li}
\authornote{Corresponding authors.}
\affiliation{%
  \institution{Shandong University}
  \country{China}
}
\author{Yuexin Ma}
\authornotemark[2]
\affiliation{%
  \institution{ShanghaiTech University}
  \country{China}
}
\author{Changhe Tu}
\affiliation{%
  \institution{Shandong University}
  \country{China}
}

\begin{abstract}
The development of intelligent robots seeks to seamlessly integrate them into the human world, providing assistance and companionship in daily life and work, with the ultimate goal of achieving human-robot symbiosis. This requires robots with intelligent interaction abilities to work naturally and effectively with humans.
However, current robotic simulators fail to support real human participation, limiting their ability to provide authentic interaction experiences and gather valuable human feedback essential for enhancing robotic capabilities.
In this paper, we introduce \textbf{SymBridge}, the first human-in-the-loop cyber-physical interactive system designed to enable the safe and efficient development, evaluation, and optimization of human-robot interaction methods. Specifically, we employ augmented reality technology to enable real humans to interact with virtual robots in physical environments, creating an authentic interactive experience. Building on this, we propose a novel robotic interaction model that generates responsive, precise robot actions in real time through continuous human behavior observation. The model incorporates multi-resolution human motion features and environmental affordances, ensuring contextually adaptive robotic responses. Additionally, SymBridge enables continuous robot learning by collecting human feedback and dynamically adapting the robotic interaction model. 
By leveraging a carefully designed system architecture and modules, \textit{SymBridge} builds a bridge between humans and robots, as well as between cyber and physical spaces, providing a natural and realistic online interaction experience while facilitating the continuous evolution of robotic intelligence. Extensive experiments, user studies, and real robot testing demonstrate the system's promising performance and highlight its potential to significantly advance research on human-robot symbiosis.
\end{abstract}


%\ccsdesc[500]{Computing methodologies~Shape modeling}
%\ccsdesc[300]{Computing methodologies~Graphics systems and interfaces}

%\acmJournal{TOG}

\keywords{Human-robot Interaction, Augmented Reality, Real-time Motion Generation}

\input{figures/fig-teaser}

%\input{macros}
\maketitle


\input{sections/1-intro-0524}
\input{sections/2-relatedWork}
\input{sections/3-system-asia}
\input{sections/4-1-HR-interaction-new}
%\input{sections/4-2-HR-collaboration}
\input{sections/5-systemeval-new}
%\input{sections/5-ablation}
%\input{sections/6-systemeval}
\input{sections/7-conclusion}

\section{Acknowledgement}
This work is supported by the National Natural Science Foundation of China (U23A20312, No.62302269, No.62206173), Shandong Provincial Natural Science Foundation (No.ZR2023QF077), Shandong Province Excellent Young Scientists Fund Program (Overseas) (No.2023HWYQ-034), Shanghai Frontiers Science Center of Human-centered Artificial Intelligence (ShangHAI), MoE Key Laboratory of Intelligent Perception and Human-Machine Collaboration (KLIP-HuMaCo).


\bibliographystyle{formats/ACM-Reference-Format}
\bibliography{Reference} 

\input{sections/8-figureonly}

\appendix


\end{document}
